---
title: "Independance first and last Names"
author: "Arthur Charpentier & Baptiste Coulmont"
date: "July 2017"
output: rmarkdown::github_document
---

Here we need to extend the correlation plot, where values are in the interval $[-1,+1]$ to geta function where values are on the real line, following a Gaussian distribution (if components are independent)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(stringr)
library(lubridate)
library(plyr)
library(data.table)
library(ggplot2)
library(ggcorrplot)
library(dplyr)
```
```{r}
ggcorrplot2 <- function(x, method = c("square", "circle"),
         outline_colour = "gray",
         colours = c("blue", "white", "red"),
         legend_title = "Pr",
         ggtheme = ggplot2::theme_minimal,
         title = "",
         tl.cex = 12, 
         tl.col = "black", tl.srt = 45,
         show_legend = TRUE){
  
  method <- match.arg(method)
  
  corr <- reshape2::melt(x, na.rm = TRUE)
  corr <- corr %>% 
    mutate(value_norm = 2*(pnorm(corr$value))-1,
           value_norm_abs = abs(value_norm),
           Var1_f = as.numeric(factor(Var1)),
           Var2_f = as.numeric(factor(Var2)))
  
  x_labs <- 
    corr %>% 
    select(Var1, Var1_f) %>% 
    unique()
  
  y_labs <- 
    corr %>% 
    select(Var2, Var2_f) %>% 
    unique()
  
  # La base du graphique
  p <- ggplot(corr, aes(x = factor(Var1_f), y = factor(Var2_f), fill = value))
  
  if (method == "square")
    p <- p + geom_tile(colour = outline_colour)
  else if(method == "circle") {
    p <- p + 
      geom_point(aes(size = value_norm_abs), shape = 21) +
      scale_size(range = c(4, 10)) +
      guides(size = FALSE)
  }

  
   p <- 
    p + scale_fill_gradient2(low = colours[1], high = colours[3], 
                           mid = colours[2], midpoint = 0,
                           space = "Lab", 
                           name = legend_title) +
    ggtheme() +
    theme(axis.text.x = element_text(angle = tl.srt, 
                                     vjust = 1, 
                                     size = tl.cex, 
                                     hjust = 1),
          axis.text.y = element_text(size = tl.cex)) + 
    coord_fixed() + 
    xlab(NULL) + ylab(NULL) +
    scale_x_discrete(breaks = x_labs$Var1_f, labels = x_labs$Var1) +
    scale_y_discrete(breaks = y_labs$Var2_f, labels = y_labs$Var2)
  
  if (title != "") 
    p <- p + ggtitle(title)
  
  if (!show_legend) 
    p <- p + theme(legend.position = "none")
   p
}
```

Let us import the datasets from our local drive

```{r}
cpttf_t <- NULL
cpttl_t <- NULL
cpttot_t <- NULLcpttf_c_t <- NULL
cpttl_c_t <- NULL
cpttot_c_t <- NULL
setwd("/home/arthur/Dropbox/Dropbox (Télécom SudParis)/homonymes")
data=read.csv("tout.csv",sep=";")
#cpttf <- count(data, wt="PRENOM1")
#cpttl <- count(data, "NOM")
#cpttf <- count(cpttf, "PRENOM1, wt_var = "freq")
#cpttl <-count(cpttl, "NOM", wt_var = "freq")
#cpttf <- arrange(cpttf, desc(n))
#cpttl <- arrange(cpttl, desc(n))
cpttl <- aggregate(data$ARR,by=list(data$NOM),FUN=length)
cpttl <- cpttl[order(cpttl$x,decreasing=TRUE),]
cpttf <- aggregate(data$ARR,by=list(data$PRENOM1),FUN=length)
cpttf <- cpttf[order(cpttf$x,decreasing=TRUE),]
names(cpttl)=c("NOM","freq")
names(cpttf)=c("PRENOM1","freq")
k=15
LP=cpttf[1:(k),]
LN=cpttl[1:(k),]
countnp <- Vectorize(function(x,y){
  sum( (data$NOM==LN$NOM[x])&(data$PRENOM1==LP$PRENOM1[y]))
})
MAT=outer(1:k,1:k,countnp)
rownames(MAT)=LN$NOM
colnames(MAT)=LP$PRENOM1
```

Use here a chi-square test to test independence betweem first and last names, on the $k=15$ most popular ones (only)

```{r}
Q=chisq.test(MAT)
Q
Q$observed
Q$expected
```

The plot is here

```{r}
ggcorrplot2(Q$stdres, method = "circle")
```