---
title: "Homonyms, French Names, dynamics"
author: "Arthur Charpentier & Baptiste Coulmont"
date: "July 2017"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

```{r}
load("/home/arthur/Dropbox/Dropbox (Télécom SudParis)/Nouveau dossier 4/charpentier.Rdata")
head(patronymes)
head(prenoms)
dim(patronymes)
x1=prenoms[,2]
x2=prenoms[,3]
x3=prenoms[,4]
statistiques=function(x,which=NA){
x[is.na(x)]=0
p1=sum(sort(x[-1],decreasing=TRUE)[1])/(sum(x))
p2=sum(sort(x[-1],decreasing=TRUE)[1:10])/(sum(x))
p3=sum(sort(x[-1],decreasing=TRUE)[1:100])/(sum(x))
sv=NA
if(which=="prenom"){
n=x[1]
vn=c(round(n/2),round(n/4),length(x[-1]))
sv=sum(vn)}
if(which=="nom"){
sv=length(x[x>0])}
c(sv/1e6,100*p1,100*p2,100*p3)
}
```

Period *1916-1940*, number of first names (in millions)
```{r}
s1=statistiques(x1,which="prenom")
s1[1]
```

use here the following rule for *rare* names : if $n$ have a rare names, $n/2$ have a unique one, and for the remaining half, we have pairs, i.e. there are $3n/4$ first names for those $n$ people

Most popular first name (in %)
```{r}
s1[2]
```
while the top ten represents (in %)
```{r}
s1[3]
```
and the top 100
```{r}
s1[4]
```

For *1941-1965* and *1966-1990*, we have (numbers in millions for the first column, and then percentages for the second colum)
```{r}
statistiques(x2,which="prenom")
statistiques(x3,which="prenom")
```

For the last name, load the datasets
```{r}
y1=patronymes[,2]
y2=patronymes[,3]
y3=patronymes[,4]
```

For the periode *1916-1940*, the number of last names (in millions) is
```{r}
s1=statistiques(y1,which="nom")
s1[1]
```

the most popular represent (in %)
```{r}
s1[2]
```
of the top list of last names. For the top 10, (in %)
```{r}
s1[3]
```
and for the top 100
```{r}
s1[4]
```

For periods *1941-1965* and *1966-1990*, we have (number in millions for the first column, and then percentage for the second one)
```{r}
statistiques(y2,which="nom")
statistiques(y3,which="nom")
```

The proportion of homonyms can be computed using the following code (first and last names are selected independently)
```{r}
prophomonymes=function(n,z){
  x=z$x
  x[is.na(x)]=0
  x0=x[-1]
  listex=c(rep(1,round(x[1]/2)),rep(2,round(x[1]/4)),x0[x0>0])
  sx=sample(1:length(listex),size=n,replace=TRUE,prob=listex)
  y=z$y
  listey=y[y>0]
  sy=sample(1:length(listey),size=n,replace=TRUE,prob=listey)
  sz=paste(sx,sy)
  t=table(sz)
  sum(t[t>1])/n}
sim=function(n,ns=50){
  P=matrix(NA,ns,3)
  for(i in 1:ns){
    P[i,1]=prophomonymes(list(x=x1,y=y1),n=n)
    P[i,2]=prophomonymes(list(x=x2,y=y2),n=n)
    P[i,3]=prophomonymes(list(x=x3,y=y3),n=n)
  }
  apply(P,2,mean)
}
```

Hence, for a group of $n=100,000$ people, the porportion of people that have an homonym is (in %), for each periods (the oldest on the left),
```{r}
sim(n=100000,ns=50)
```
with 50 simulations in those Monte Carlo simulations
```{r}
P=matrix(NA,5,3)
P[1,]=sim(10000,50)
P[2,]=sim(20000,50)
P[3,]=sim(50000,50)
P[4,]=sim(100000,50)
P[5,]=sim(200000,50)
```

To visualize it, use
```{r}
proba=data.frame(annees=rep(c("1916-1940","1941-1965","1966-1990"),5),
                 proba=c(P[1,],P[2,],P[3,],P[4,],P[5,])*100,
                 Taille=as.factor(rep(c(10000,20000,50000,100000,200000),each=3)))
library(ggplot2)
ggplot(proba,aes(annees,proba,color=Taille,group=Taille))+geom_point()+geom_line()+
  scale_y_log10()+ylab("Probabilité (%)")+xlab("") + theme(legend.position="top")
```

